### 2019-10-10 tim-lucas-model-ensembles.tex
Add coverage table.

\begin{table}[h!]
\caption{Covarage of 80\% credible intervals. }
\centering
\begin{tabular}{llrrrr}
CV & Country &  Enviro & ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Random &  Colombia &  \\
 Spatial &  Colombia &  \\
 Random &  Madagascar &  \\
 Spatial &  Madagascar & \\
 Random &  Senegal & \\
 Spatial &  Senegal &  \\
 Random &  Indonesia &  \\
 Spatial &  Indonesia &   \\
\end{tabular}
\label{t:results2}
\end{table}

>>>>

\begin{table}[h!]
\caption{Covarage of 80\% credible intervals. Values outside 0.7--0.9 are shown in bold.}
\centering
\begin{tabular}{llrrrrr}
CV & Country &  Enviro & ML\textsubscript{l} &  Enviro + ML\textsubscript{l} & ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Colombia & Random & \textbf{0.28} & \textbf{0.28} & \textbf{0.29} & \textbf{0.29} & \textbf{0.29} \\
 Madagascar &  Random & 0.80 & 0.77& 0.75& 0.77& 0.76 \\
 Senegal & Random &0.79 & 0.79& 0.79& 0.79& 0.82 \\
 Indonesia & Random &0.80 & 0.81& 0.78& 0.79& 0.77  \\
 Colombia &  Spatial & \textbf{0.31} & \textbf{0.34}  & \textbf{0.32} & \textbf{0.34} & \textbf{0.34}  \\
 Madagascar & Spatial & \textbf{0.65} & 0.74& 0.70& 0.75 & 0.76   \\
 Senegal & Spatial & 0.85 & \textbf{0.91}& 0.85& \textbf{0.94} & 0.85  \\
  Indonesia & Spatial & 0.80 & 0.78& 0.78& 0.76& 0.75  \\
\end{tabular}
\label{t:results2}
\end{table}
